Innovations Report: Procedural Fur System

### 2018-03-16 docs/paper.tex
more docs & shader tweak
more on docs

\section{Introduction} \label{sec:introduction}
Introduction Text.

@@

\begin{enumerate}
\item Generate a uniform random number in the range [0.0 - 1.0].
\end{enumerate}

The most common way of storing OBJ data in OpenGL buffers, as described in \cite{objLoading}, is to use a \verb|GL_ARRAY_BUFFER| object to store the vertex data and a \verb|GL_ELEMENT_ARRAY_BUFFER| to store the indices of the \verb|GL_ARRAY_BUFFER| that make up each face. However for ease of use in compute shaders I decided instead to store each face in a \verb|GL_SHADER_STORAGE_BUFFER|, where each face consists of three sets of positions, normals, and texture coordinates. Whilst this is less efficient, I found that the overhead in GPU memory usage was negligible, and that this method allowed for much simpler usage in a compute shader.

@@

>>>>

\section{Introduction} \label{sec:introduction}
Introduction Text.
\subsection{Related Work} \label{sec:related}
nvidia hairworks

@@

% \begin{enumerate}
% \item Generate a uniform random number in the range [0.0 - 1.0].
% \end{enumerate}

% \begin{algorithm}
% \begin{algorithmic}[1]
% \Procedure{Naive Random Distributionr}{}
% \For{k to k}
% \EndFor
% \EndProcedure
% \end{algorithmic}
% \end{algorithm}

\subsubsection{Compute Shaders} \label{sec:compute shaders}

In order to get this distribution process running on the GPU, I needed to allocate and store data for both the Mesh and Curves in OpenGL buffers, for later use in a compute shader. The most common way of storing OBJ data in OpenGL buffers, as described in \cite{objLoading}, is to use a \verb|GL_ARRAY_BUFFER| object to store the vertex data and a \verb|GL_ELEMENT_ARRAY_BUFFER| to store the indices of the \verb|GL_ARRAY_BUFFER| that make up each face. However for ease of use in compute shaders I decided instead to store each face in a \verb|GL_SHADER_STORAGE_BUFFER|, where each face consists of three sets of positions, normals, and texture coordinates. Whilst this is less efficient, I found that the overhead in GPU memory usage was negligible, and that this method allowed for much simpler usage in a compute shader. Allocating a buffer for the Curves data was much simpler as it consisted of an array of 'Curve' structs, each consisting of 5 vertices. Listing~\ref{lst:buffers} shows how these buffers were accessed from within the compute shaders; note how all of the \texttt{vec3} values have been padded to \texttt{vec4}, as the \texttt{std430} layout qualifier requires an alignment of 16 bytes.

\begin{lstlisting}[language=GLSL, label={lst:buffers}, caption={Extract from the Distributor compute shader, showing how the Mesh and Curves buffers are accessed.}]
struct Face
{
	vec4 position[3];
	vec4 normal[3];
	vec4 uv[3];
};

struct Curve
{
	vec4 position[5];
};

layout (std430, binding = 0) buffer facesBuffer
{
	Face faces[];
};

layout (std430, binding = 1) buffer curvesBuffer
{
	Curve curves[];
};
\end{lstlisting}

\subsubsection{Curve Operators} \label{sec:operators}

@@

\begin{figure}[htbp]\centering
\begin{center}
\begin{tabular}{||c||c|c|c||}
\hline
Mesh Triangle Count & Primitive Count & CPU Time (ms) & GPU Time (ms)\\
\hline
\hline
16 (Triangle Strip) & 10,000 & 2 - 5 & 1 - 2\\
\hline
 - & 100,000 & 18 - 41 & 8 - 24\\
\hline
 - & 1,000,000 & 120 - 150 & 77 - 110\\
\hline
4968 (Stanford Bunny) & 10,000 & 173 - 211 & 1 - 2\\
\hline
 - & 100,000 & 1718 - 1756 & 12 - 30\\
\hline
 - & 1,000,000 & 17218 - 17259 & 82 - 112\\
\hline
\end{tabular}
\caption{\label{figure:distributionPerformance} Performance metrics showing time taken to distribute varying numbers of primitives, on meshes of varying triangle counts. The system used had an Intel Core i7-6700 CPU, and an NVIDIA GTX1080 GPU.}
\end{center}
\end{figure}

\begin{figure}[htbp]\centering
\begin{center}
\begin{tabular}{||c|c||}
\hline
Mesh Triangle Count & GPU Time (ms)\\
\hline
\hline
16 (Triangle Strip) & 18 - 20\\
\hline
4968 (Stanford Bunny) & 33 - 45\\
\hline
14067 (Utah Teapot) & 76 - 92\\
\hline
\end{tabular}
\caption{\label{figure:fullPerformance} Performance metrics showing the time taken to perform a full graph evaluation on a complex setup, as seen in INSERT PIC, for meshes of varying triangle counts.}
\end{center}
\end{figure}
